Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-16 latex/paper.tex
cited datasets

\begin{itemize}
	\item \textit{Hyperspectral Imaging}:
	\LM{DC: https://engineering.purdue.edu/~biehl/MultiSpec/hyperspectral.html}
	For Hyperspectral imaging, we chose the Hyperspectral digital imagery collection experiment (HYDICE) image of the Washington DC Mall. We will refer
	to this dataset as \hyper{}.

@@

	Larger hyperspectral datasets tend to not grow larger than around 200 spectral bands and have millions or billions of pixels. So, scaling is 
	limited for this dataset given our data distribution scheme.
	\item \textit{Image Classification}:
	\LM{https://www.kaggle.com/c/siim-isic-melanoma-classification/data}
	Image Classification datasets contain tens of thousands of images of equal size. The dataset we chose is the SIIM-ISIC Melanoma classification
	dataset, which we will refer to as \image{}. \image{} consists of $33126$ RGB training images equally sized at $1024 \times 1024$. Unlike with hyperspectral imaging, the resulting
	matrix used in H2NMF consists of image pixels along the rows and individual images along the columns. So, the resulting sized matrix is
	$3145728 \times 33126$, which is approximately 800GB in size.

>>>>

\begin{itemize}
	\item \textit{Hyperspectral Imaging}:
	For Hyperspectral imaging, we chose the Hyperspectral digital imagery collection experiment (HYDICE) image of the Washington DC Mall. We will refer
	to this dataset as \hyper{}\cite{DC-HYDICE}.

@@

	Larger hyperspectral datasets tend to not grow larger than around 200 spectral bands and have millions or billions of pixels. So, scaling is 
	limited for this dataset given our data distribution scheme.
	\item \textit{Image Classification}:
	Image Classification datasets contain tens of thousands of images of equal size. The dataset we chose is the SIIM-ISIC Melanoma classification
	dataset, which we will refer to as \image{}\cite{SIIM-ISIC}. \image{} consists of $33126$ RGB training images equally sized at $1024 \times 1024$. Unlike with hyperspectral imaging, the resulting
	matrix used in H2NMF consists of image pixels along the rows and individual images along the columns. So, the resulting sized matrix is
	$3145728 \times 33126$, which is approximately 800GB in size.
